Make any stupid plot you want

### 2021-01-20 draft/sections/math.tex
closing out k

Many

with transition functions that are maps from the fiber to the fiber along the edges. can also fold in if monoid is commutative on transition function:

>>>>

A fiber bundle is trivial if $E = K\times F$, which means that the fibers $F$ are the same over every $k$. We can make many non-trivial spaces locally trivial by breaking up the total space $E$ over local neighborhoods $U \subset K$ such that the fibers are equivalant. An example of a non-trivial fiber bundle is a mobius strip, where because of the twist some fibers are $\left[0,1\right]$ and others are $\left[1,0\right]$ such that we cannot construct a global map of which edge is 0 and which edge is 1.  In figure ~\ref{fig:data_base_transition}, the mobius strip is cut into two rectangular base spaces over $K=\{e_1, e_2\}$. We define transition functions from the fiber to the fiber along the edges of the rectangles such that we can glue these rectangles together to reform the mobius strip. A constraint we impose on the transition functions is that the monoid actions are commutative
-% need more detail please on commutativty
